---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# pfft

The goal of pfft is to ...

## Installation

You can install pfft from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mdsumner/pfft")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```



Polygon finder for triangles

This workflow came from anglr, the current scheme is to triangulate set-wide, on the entire layer and then find out which polygon each triangle belongs to. This is because polygons that wrap around a void but only touch at a single vertex end up with that void being kept as only the regions inside holes was being removed. 

If we do it set-wide we can't check each feature individually (a feature might be inside a hole of another feature), and we can't sensibly normalize triangles that fall into overlapping features. 

Together this gives the best of all (that's the theory, today!) and solves a bunch of lingering problems that anglr has. 

If we provide a native point-in-polygon routine here then we can abandon dependencies that bring in other unused libs. 

This looks good, though maybe geometry or ptinpoly or something like that: 

https://stackoverflow.com/a/36684485/355270


This also means we can use z-fighting, easily visible with rgl, to indicate when we have overlapping features - and also ilustrate how we need to de-normalize for discrete features in 3D, etc. etc. 

```{r, webgl=TRUE}
library(raster)
library(spex)
library(sf)
library(dplyr)
library(pfft)
library(rgl)
data("holey", package = "spbabel")
#x <- st_as_sf(spbabel::sp(holey))
library(sf)
x <- read_sf(system.file("shape/nc.shp", package="sf"))
#data("minimal_mesh", package = "silicate")
#x <- minimal_mesh
max_area <- NULL
p <- silicate::PATH(x)  
RTri <- edge_RTriangle(p)
ptm <- path_triangle_map(p, RTri)


triangle <- tibble::tibble(triangle_ = silicate::sc_uid(nrow(RTri$T)), triangle_idx = 1:nrow(RTri$T))
ptm[["triangle_"]] <- triangle[["triangle_"]][ptm[["triangle_idx"]]]
ptm <- dplyr::inner_join(ptm, p[["path"]][c("path_", "object_", "subobject")])
ptm <- ptm %>% group_by(object_,  subobject, triangle_idx) %>% mutate(n = n()) %>% ungroup()  %>% dplyr::filter(n < 2)


o <- p[["object"]]
t <- ptm %>% #ptm %>% dplyr::inner_join(p$path %>% dplyr::select(object_, path_)) %>% 
  dplyr::select(object_, triangle_)
remove_idx <-  setdiff(1:nrow(RTri$T), ptm$triangle_idx)
ptm <- ptm %>% dplyr::arrange(triangle_idx)
if (length(remove_idx) > 0) TT <- RTri$T[-remove_idx, ] else TT <- RTri$T
tXv <- tibble::tibble(vertex_ = p[["vertex"]][["vertex_"]][t(TT)], 
                      triangle_ = rep(ptm[["triangle_"]], each = 3))

v <- p[["vertex"]]
outlist <- list(o = o, t = t, tXv = tXv, v = v)
 class(outlist) <- "trimesh"
  
library(anglr)
rgl::rgl.clear()
plot(outlist)
rgl::rglwidget()
  
  
```


```R
# gibble_pip <- function(pts, gm, coords) {
#   object_id <- rep(seq_len(nrow(gm)), gm[["nrow"]])
#   tibble::tibble(ipoly = sp::over(SpatialPoints(as.matrix(pts)), 
#                                   sp::SpatialPolygons(purrr::imap(split(coords, object_id), 
#                                                                   ~ sp::Polygons(list(sp::Polygon(as.matrix(.x))), .y)))
#   ))
# }
```
# Dev

```R

tools::package_native_routine_registration_skeleton("../pfft", "src/init.c",character_only = FALSE)
```
